Code Clones: To refactor or not to refactor?

### 2020-05-09 ase/paper.tex
Updates from Overleaf

% Experimental setup: how we validated that we fixed the problem
To simulate such refactorings in a controlled environment, we create a tool that can automatically refactor a subset of duplication problems in Java source code. This subset is selected because not all clones can easily be automatically refactored, so we identify and define those that can. Using these definitions we can extract a sufficiently large dataset of refactored clones to perform our analyses. Our tool refactors 13k clones over 2k open-source Java projects and measures the delta maintainability scores of the refactoring.

@@

Over a corpus of 2,267 Java project our tool refactors 12,710 clone classes. We find that the main influencing factor on maintainability when refactored is clone volume. %We define token volume as the combined number of tokens in all clone instances in a clone class. %When refactoring clones with a very small token volume, we found that the maintainability decreases when such clones are refactored. 
The average clone with a volume of 63 or more tokens improves maintainability when refactored. The other factor with a major influence on maintainability is the number of parameters that are required for the extracted method. We find that if a clone requires more than 2 parameters in the extracted method, it is more likely to decrease maintainability.

>>>>

% Experimental setup: how we validated that we fixed the problem
To conduct such refactorings in a controlled environment, we create a tool that can automatically refactor a set of duplication problems in Java source code. This set is selected because not all clones can easily be automatically refactored, so we identify and define those that can. Using these definitions we can extract a sufficiently large dataset of refactored clones to perform our analyses. Our tool refactors 13k clones over 2k open-source Java projects and measures the delta maintainability scores of the refactoring.

@@

Over a corpus of 2,267 Java projects our tool refactors 12,710 clone classes. We find that the main influencing factor on maintainability when refactored is clone volume. %We define token volume as the combined number of tokens in all clone instances in a clone class. %When refactoring clones with a very small token volume, we found that the maintainability decreases when such clones are refactored. 
The average clone with a volume of 63 or more tokens improves maintainability when refactored. The other factor with a major influence on maintainability is the number of parameters that are required for the extracted method. We find that if a clone requires more than 2 parameters in the extracted method, it is more likely to decrease maintainability.
